### 2019-09-30 NA_paper/manuscript_II/NA_temp/qso_paperII.tex
Update abstract by John

\begin{abstract}
Supermassive black holes (BH) harbor at the center of galaxies with their masses (\mbh) correlated to the properties of the host galaxies, including absolute magnitude ($Mag$) and stellar mass (\mstar) known as scaling relations (i.e., \mbh-\lhost, \mbh-\mstar). 
 %Observational results have indicated evidence that this correlation evolves with cosmic time, suggesting a scenario that the BH growth predates their host. In theory, positive evolution of BH is also predicted by several simulation projects independently.
So far, the simulations have reproduced these relations which have a good agreement to the observational sample from local to intermediate redshift ($z<1$). It is crucial to extend this study to higher redshift ($z>1$), where the predicted relations are more sensitive to the initial assumptions and any inconsistency would help to pinpoint the incorrect ones.
To this end, we use a sample of 32 X-ray-selected broad-line (type-1) AGNs at $1.2 < z < 1.7$ ($\sim 8.5-10$ billion years ago) to make a direct comparison to the predicted sample using two independent state-of-the-art simulation projects: MassiveBlack-II (MBII) and semi-analytic models (SAM). We adopt \hst\ to take the  AGN image in multi-bands to derive the trustworthy host galaxies properties and use the reliable broad \halpha\ emission lines by Subaru/FMOS to estimate the \mbh. Taking the selection bias into account, %by adopting the same selection function to choose the simulating sample,
we find that both MBII and SAM agree well with the data, in terms of the central distribution. However, when taking the measurement uncertainty into account and comparing the scatter, the observations are more consistent with the MBII sample ($\sim0.3$~dex), than the SAM one ($\sim0.7$~dex). In this respect, our observational constraints are able to distinguish the two models, indicating that the recipe by MBII (AGN feedback driven) is more rather than the SAM one (galaxy interaction driven). Moreover, the intrinsic scatter of our high-$z$ sample is not larger than the local sample, which is against the central limit theorem (a purely stochastic process). To some extent, our result attests that there has to be a causal link between SMBH and its host galaxy to induce an ordering so that the more massive black holes are tightly linked to the more massive galaxies.

>>>>

\begin{abstract}
Supermassive black holes (BH) are known to reside at the center of massive galaxies. In the local Universe, BH masses (\mbh) are tightly correlated to the properties of their host galaxies, including absolute magnitude ($Mag$) and stellar mass (\mstar), known as scaling relations (i.e., \mbh-\lhost, \mbh-\mstar) that are not yet fully understood. 
 %Observational results have indicated evidence that this correlation evolves with cosmic time, suggesting a scenario that the BH growth predates their host. In theory, positive evolution of BH is also predicted by several simulation projects independently.
Even so, simulations can reproduce these relations over the last eight billion years ($z\lesssim1$). However, it is crucial to extend comparisons between observational data and simulations to earlier cosmic epochs ($z>1$), where the predicted relations are more sensitive to the initial assumptions and any inconsistency would help to pinpoint missing physics.
For this purpose, we have a unique sample of 32 broad-line Active Galactic Nuclei (AGN) at $1.2 < z < 1.7$ ($\sim 8.5-10$ billion years ago) with the broad \halpha\ emission line, as detected by Subaru/FMOS, providing an accurate assessment of \mbh ~while multi-band \hst\ imaging is used to derive the host galaxies properties (e.g., \mstar).
We directly compare this sample with two independent state-of-the-art simulations: MassiveBlack-II (MBII) and a semi-analytic model (SAM).  Taking the selection biases into account, %by adopting the same selection function to choose the simulating sample,
we find that both MBII and SAM agree well with the data, in terms of the central distribution. However, when considering measurement uncertainty and the scatter in the scaling relations, the observations are significantly more consistent with the MBII sample ($\sim0.3$~dex), than the SAM ($\sim0.7$~dex). In this respect, our observational constraints are able to distinguish between the two models, indicating that the recipe implemented by MBII (i.e., growth regulation through AGN feedback) is preferred over the SAM that does not include AGN feedback. Moreover, the intrinsic scatter of our high-$z$ sample is comparable to the local sample thus counter to the expectation from a scenario based on the central limit theorem (a purely stochastic process). To some extent, our result attests that there has to be a causal link between SMBH and its host galaxy to induce an ordering so that the more massive black holes are tightly linked to the more massive galaxies.
